A Partitioning Algorithm for Maximum Common Subgraphs\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-02-15 paper/paper.tex
New abstract

\begin{abstract}
    Maximium Common Subgraph (MCS) is the problem of finding a
    graph of maximium order that is an induced subgraph of each of the two input
    graphs.  We introduce \McSplit, a branch and bound algorithm that
    uses a vertex-labelling scheme to compactly represent the subsets of
    vertices that may be matched together to create a larger common subgraph.
    The new algorithm explores the same search space as the existing CP-FC
    algorithm, but requires only \BigO{n^2} space in total and \BigO{n} time
    for each recursive call, greatly improving on all existing algorithms for
    the problem. Experimental results using two large graph databases show that \McSplit\ is
    more than an order of magnitude faster than the leading existing algorithms
    on undirected, unlabelled graphs, including the problem
    variant in which the subgraph must be connected.
\end{abstract}

>>>>

\begin{abstract}
    We introduce a new branch and bound algorithm for the maximum common
    subgraph and maximum common connected subgraph problems which is based
    around vertex labelling and partitioning. Our method in some ways resembles
    a traditional constraint programming approach, but uses a novel compact
    domain store and supporting inference algorithms which dramatically reduce
    the memory and computation requirements during search, and allow better
    dual viewpoint ordering heuristics to be calculated cheaply.  Experiments
    show a speedup of more than an order of magnitude over the state of the
    art, and demonstate that we can operate on much larger graphs without
    running out of memory.
\end{abstract}
